### 2012-01-12 paper.tex
Worked on the introduction and experimental sections

\twocolumn[
  \begin{@twocolumnfalse}
\noindent\LARGE{\textbf{Oscillations in CO-oxidation Catalysts at Atmospheric Pressures$^\dag$}}
\vspace{0.6cm}

@@

Oxidation of CO is a classic model system for testing catalytic properties of various materials. It was shown already in 1985 (REF) that this reaction will show oscilaltory behaviour under UHV conditions due to surface reconstructions having large influence on the catalytic activity of the surface. However, this is a phenomenon that is only observed under UHV-condition, under higher pressures these kinds of reconstructions will happen. In this paper we show sustained catalytic oscilations on Platinum nano particles that due to their sometimes extremely long time-scales cannot be a surface phenomenon, but must involve a bulk oxidation of the nanoparticle. 
Similar phenomeon of oscillations of CO oxidation Pt has been seen earlier on thin-films \cite{Lund2000}, single crystals \cite{Hendriksen2005} and in macroscopic flow-reactors \cite{Singh2010}, but to our knowledge never before on nano particles.

\section{Experimental Methods}
The measurents are done in a silicon-fabricated microreactor, developed here at CINF \cite{Henriksen2009}. The reactor consists of a two inlets, a long mixing zone for the incoming gases and a reactor of total volume of $240\,$nL. The reactor is able to operate at a pressure range og 0-2.5\,bar. The gases is supplied through ordinary flow controllers capable of controlling flow in the range of a few mL/min. The flow is reduced to a value capable of being fed into a mass-spectrometer by passing most of the flow through an outlet connected to a pressure controller. A small part of the flow is led into the reactor chamber and via a $5.4\,\mu$m wide capillary further into UHV chamber equiped with a quadropole mass spectrometer. The design ensures that all gas exposed to the catalyst under investigation is also measured in the mass spectrometer ensures a very high sensitivity of the device. When an evacuated microreactor is mounted, the base pressure of the UHV chambe is $\sim5\times10^{-9}\,$mbar and when operating at $1\,$bar in the reactor the pressure is $\sim5\times10^{-7}\,$mbar.

The reactor is heated by a Pt heating element evaporated on the backside that at the same time acts as an RTD to measure the temperature.

\section{Sample preparation}
The samples was made by depositing a very small amount of size-selcted clusters from a quadropole cluster source (REF!) onto the microreactores. Typical sizes are in the order of 3-9\,nm and the coverage is kept at approximately 0.1\% geometric coverage, found by measuring the current from the charged clusters landing on the reactor. After deposition the reactor is anonicly bonded to a pyrex lid while keeping the reactor area cold by mounting the reactor on a cooling block and heating the rest of the sample to $\sim350\,^\circ$C \cite{Vesborg2010}

>>>>

\twocolumn[
  \begin{@twocolumnfalse}
\noindent\LARGE{\textbf{Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure$^\dag$}}
\vspace{0.6cm}

@@

Because of its industrial importance CO oxidation on transition metal surfaces has been widely studied as both industrial catalyst and as a model system for testing catalytic properties of materials (REF, Ertl?). Despite intensive studies this reaction is still not understood and shows interesting new and interesting features.

It has previously been shown (REF) that CO oxidation will show oscillatory behavior on single crystals on palladium \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and bare metal surface. CO oxidation oscillations on has also been observed on thin-films \cite{Lund2000} and in macroscopic flow reactors \cite{Singh2010} but never on size selected platinum nanoparticles at atmospheric pressures for prolonged periods of time.

\section{Experimental Methods}
\subsection{$\mu$-reactors}
Reaction data was performed in silicon-based microreactors developed in-house \cite{Henriksen2009}. The reactor consists of a two inlets, a long mixing zone for the reaction gases to allow for diffusional mixing, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide capillary used for probing the gases from the reactor volume. The reactor is sealed from atmosphere by anodic bonding of a pyrex lid to the silicon reactor is able to operate at a pressure range of 0-2.5\,bar. The reaction gases is supplied through flow controllers capable of controlling flow in the range of a 1-10 mL/min. The capillary flow fed into a quadropole mass-spectrometer while any extra gas from the inlets are passed through the outlet connected to a pressure controller to control the reactor pressure. The design ensures that all gas exposed to the catalyst under investigation is measured by the mass spectrometer ensuring a high sensitivity of the device. When an evacuated microreactor is mounted, the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and when operating at $1\,$bar in the reactor the pressure is $\sim5\times10^{-7}\,$mbar.

The reactor is heated by joule heating of platinum strip evaporated on the backside of the reactor volume. The introduction of two additional contacts on the backside of the reactor allows for 4 wire measurements of the resistance of the platinum strip using it as a RTD for temperature measurement of the reactor volume.

\subsection{Platinum nanoparticle deposition}
Platinum nanoparticles were deposited from a size-selected cluster source (REF!). Clusters are produced by impinging argon ions on a metal target and condensing these in a cold gas. The cluster are subsequently size-selected by a quadropole mass selection filter. Typical sizes are 3-9\,nm and the coverage is kept at approximately 0.1\% geometric coverage determined by measuring the current on the reactor. After deposition the reactor is anodicly cold-bonded \cite{Vesborg2010} to a pyrex lid to avoid sintering of the nanoparticles.
